\begin{thebibliography}{100}

\bibitem{curtis_mahout:_2011} Andrew~R. Curtis, Wonho Kim, and Praveen Yalagandula.
\newblock Mahout: {Low}-overhead datacenter traffic management using
  end-host-based elephant detection.
\newblock In {\em {INFOCOM}, 2011 {Proceedings} {IEEE}}, pages 1629--1637.
  IEEE, 2011.

\bibitem{al-fares_hedera:_2010} Mohammad Al-Fares, Sivasankar Radhakrishnan, Barath Raghavan, Nelson Huang, and
  Amin Vahdat.
\newblock Hedera: {Dynamic} flow scheduling for data center networks.
\newblock In {\em Nsdi}, volume~10, pages 19--19, 2010.

\bibitem{jun_ddos_2014} Jae-Hyun Jun, Cheol-Woong Ahn, and Sung-Ho Kim.
\newblock {DDoS} attack detection by using packet sampling and flow features.
\newblock pages 711--712. ACM Press, 2014.

\bibitem{jasek_usage_2013} Roman Ja{\v s}ek, Anna Szmit, and Maciej Szmit.
\newblock Usage of {Modern} {Exponential}-{Smoothing} {Models} in {Network}
  {Traffic} {Modelling}.
\newblock In Ivan Zelinka, Guanrong Chen, Otto~E. R{\"o}ssler, Vaclav Snasel,
  and Ajith Abraham, editors, {\em Nostradamus 2013: {Prediction}, {Modeling}
  and {Analysis} of {Complex} {Systems}}, pages 435--444, Heidelberg, 2013.
  Springer International Publishing.

\bibitem{munz_traffic_2010} Gerhard M{\"u}nz.
\newblock {\em Traffic anomaly detection and cause identification using
  flow-level measurements}.
\newblock Number 2010,06 in Network architectures and services. Network
  Architectures and Services, Techn. Univ. M{\"u}nchen, M{\"u}nchen, 2010.
\newblock OCLC: 845870015.

\end{thebibliography}

%%%%% CLEAR DOUBLE PAGE!
\newpage{\pagestyle{empty}\cleardoublepage}
