\begin{thebibliography}{100}

\bibitem{sims_david_carousels_2011} David Sims.
\newblock Carousel's {Expert} {Walks} {Through} {Major} {Benefits} of
  {Virtualization}, July 2011.

\bibitem{sampaio_energy-efficient_2015} Altino Manuel~Silva Sampaio.
\newblock {\em Energy-efficient and {SLA}-based {Management} of {IaaS} {Cloud}
  {Data} {Centers}}.
\newblock {PhD} {Thesis}, Universidade do Porto (Portugal), 2015.

\bibitem{bakhshi_user-centric_2017} Taimur Bakhshi.
\newblock {\em User-{Centric} {Traffic} {Engineering} in {Software} {Defined}
  {Networks}}.
\newblock {PhD} {Thesis}, University of Plymouth, 2017.

\bibitem{open_networking_foundation_sdn_2014} {Open Networking Foundation}.
\newblock {SDN} {Architecture} {Overview}.
\newblock Technical TR\_SDN ARCH Overview 1.1 1111 2014, Open Networking
  Foundation, November 2014.

\bibitem{shin_software-defined_2012} Myung-Ki Shin, Ki-Hyuk Nam, and Hyoung-Jun Kim.
\newblock Software-defined networking ({SDN}): {A} reference architecture and
  open {APIs}.
\newblock pages 360--361. IEEE, October 2012.

\bibitem{open_networking_foundation_openflow_2015} {Open Networking Foundation}.
\newblock {OpenFlow} {Switch} {Specification} {Version} 1.3.5 ( {Protocol}
  version 0x04 ), March 2015.

\bibitem{broadcom_corporation_openflow_2017} {Broadcom Corporation}.
\newblock {OpenFlow}{\texttrademark} {Data} {Plane} {Abstraction} ({OF}-{DPA}):
  {Abstract} {Switch} {Specification}, January 2017.

\bibitem{sezer_are_2013} Sakir Sezer, Sandra Scott-Hayward, Pushpinder~Kaur Chouhan, Barbara Fraser,
  David Lake, Jim Finnegan, Niel Viljoen, Marc Miller, and Navneet Rao.
\newblock Are we ready for {SDN}? {Implementation} challenges for
  software-defined networks.
\newblock {\em IEEE Communications Magazine}, 51(7):36--43, 2013.

\bibitem{raz_2014_2014} Danny Raz, International~Federation for Information~Processing, Institute
  of~Electrical {and} Electronics~Engineers, Communications Society, and
  Computer Society, editors.
\newblock {\em 2014 10th {International} {Conference} on {Network} and
  {Service} {Management} ({CNSM} 2014): {Rio} de {Janeiro}, {Brazil}, 17 - 21
  {November} 2014 ; [including workshop papers]}.
\newblock IEEE, Piscataway, NJ, 2014.
\newblock OCLC: 931888885.

\bibitem{nunes_survey_2014} Bruno Astuto~A. Nunes, Marc Mendonca, Xuan-Nam Nguyen, Katia Obraczka, and
  Thierry Turletti.
\newblock A {Survey} of {Software}-{Defined} {Networking}: {Past}, {Present},
  and {Future} of {Programmable} {Networks}.
\newblock {\em IEEE Communications Surveys \& Tutorials}, 16(3):1617--1634,
  2014.

\bibitem{vishnoi_effective_2014} Anilkumar Vishnoi, Rishabh Poddar, Vijay Mann, and Suparna Bhattacharya.
\newblock Effective switch memory management in {OpenFlow} networks.
\newblock pages 177--188. ACM Press, 2014.

\bibitem{phemius_disco:_2014} Kevin Phemius, Mathieu Bouet, and Jeremie Leguay.
\newblock {DISCO}: {Distributed} multi-domain {SDN} controllers.
\newblock pages 1--4. IEEE, May 2014.

\bibitem{khondoker_feature-based_2014} Rahamatullah Khondoker, Adel Zaalouk, Ronald Marx, and Kpatcha Bayarou.
\newblock Feature-based comparison and selection of {Software} {Defined}
  {Networking} ({SDN}) controllers.
\newblock pages 1--7. IEEE, January 2014.

\bibitem{berde_onos:_2014} Pankaj Berde, William Snow, Guru Parulkar, Matteo Gerola, Jonathan Hart, Yuta
  Higuchi, Masayoshi Kobayashi, Toshio Koide, Bob Lantz, Brian O'Connor, and
  Pavlin Radoslavov.
\newblock {ONOS}: towards an open, distributed {SDN} {OS}.
\newblock pages 1--6. ACM Press, 2014.

\bibitem{project_floodlight_floodlight_2017} {Project Floodlight}.
\newblock Floodlight {Is} an {Open} {SDN} {Controller}, 2017.

\bibitem{medved_opendaylight:_2014} Jan Medved, Robert Varga, Anton Tkacik, and Ken Gray.
\newblock {OpenDaylight}: {Towards} a {Model}-{Driven} {SDN} {Controller}
  architecture.
\newblock pages 1--6. IEEE, June 2014.

\bibitem{bierman_restconf_2017} Andy Bierman, Martin Bjorklund, and Kent Watsen.
\newblock {\em {RESTCONF} {Protocol}}.
\newblock Number 8040 in Request for {Comments}. RFC Editor, January 2017.
\newblock Published: RFC 8040.

\bibitem{akyildiz_research_2016} Ian~F. Akyildiz, Ahyoung Lee, Pu~Wang, Min Luo, and Wu~Chou.
\newblock Research challenges for traffic engineering in software defined
  networks.
\newblock {\em IEEE Network}, 30(3):52--58, May 2016.

\bibitem{mousavi_early_2015} Seyed~Mohammad Mousavi and Marc St-Hilaire.
\newblock Early detection of {DDoS} attacks against {SDN} controllers.
\newblock pages 77--81. IEEE, February 2015.

\bibitem{curtis_mahout:_2011} Andrew~R. Curtis, Wonho Kim, and Praveen Yalagandula.
\newblock Mahout: {Low}-overhead datacenter traffic management using
  end-host-based elephant detection.
\newblock In {\em {INFOCOM}, 2011 {Proceedings} {IEEE}}, pages 1629--1637.
  IEEE, 2011.

\bibitem{brauckhoff_impact_2006} Daniela Brauckhoff, Bernhard Tellenbach, Arno Wagner, Martin May, and Anukool
  Lakhina.
\newblock Impact of packet sampling on anomaly detection metrics.
\newblock In {\em Proceedings of the 6th {ACM} {SIGCOMM} conference on
  {Internet} measurement}, pages 159--164. ACM, 2006.

\bibitem{noauthor_recommendation_1992} Recommendation {X}.700 {MANAGEMENT} {FRAMEWORK} {FOR} {OPEN} {SYSTEMS}
  {INTERCONNECTION} ({OSI}) {FOR} {CCITT} {APPLICATIONS}, September 1992.

\bibitem{fedor_simple_1990} Mark Fedor, James~R. Davin, Martin~Lee Schoffstall, and Dr~Jeff~D. Case.
\newblock {\em Simple {Network} {Management} {Protocol} ({SNMP})}.
\newblock Number 1157 in Request for {Comments}. RFC Editor, May 1990.
\newblock Published: RFC 1157.

\bibitem{rose_structure_1990} Dr~Marshall~T. Rose and Keith McCloghrie.
\newblock {\em Structure and identification of management information for
  {TCP}/{IP}-based internets}.
\newblock Number 1155 in Request for {Comments}. RFC Editor, May 1990.
\newblock Published: RFC 1155.

\bibitem{rose_management_1990} Dr~Marshall~T. Rose and Keith McCloghrie.
\newblock {\em Management {Information} {Base} for network management of
  {TCP}/{IP}-based internets}.
\newblock Number 1156 in Request for {Comments}. RFC Editor, May 1990.
\newblock Published: RFC 1156.

\bibitem{schonwalder_overview_2003} J{\"u}rgen Sch{\"o}nw{\"a}lder.
\newblock {\em Overview of the 2002 {IAB} {Network} {Management} {Workshop}}.
\newblock Number 3535 in Request for {Comments}. RFC Editor, May 2003.
\newblock Published: RFC 3535.

\bibitem{popa_cost_2010} Lucian Popa, Sylvia Ratnasamy, Gianluca Iannaccone, Arvind Krishnamurthy, and
  Ion Stoica.
\newblock A {Cost} {Comparison} of {Datacenter} {Network} {Architectures}.
\newblock In {\em Proceedings of the 6th {International} {COnference}},
  Co-{NEXT} '10, pages 16:1--16:12, New York, NY, USA, 2010. ACM.

\bibitem{bisdn_gmbh_software_2017} {BISDN GmbH}.
\newblock Software - {Defined} {Cloud} {Networking}, 2017.

\bibitem{jasek_usage_2013} Roman Ja{\v s}ek, Anna Szmit, and Maciej Szmit.
\newblock Usage of {Modern} {Exponential}-{Smoothing} {Models} in {Network}
  {Traffic} {Modelling}.
\newblock In Ivan Zelinka, Guanrong Chen, Otto~E. R{\"o}ssler, Vaclav Snasel,
  and Ajith Abraham, editors, {\em Nostradamus 2013: {Prediction}, {Modeling}
  and {Analysis} of {Complex} {Systems}}, pages 435--444, Heidelberg, 2013.
  Springer International Publishing.

\bibitem{munz_traffic_2010} Gerhard M{\"u}nz.
\newblock {\em Traffic anomaly detection and cause identification using
  flow-level measurements}.
\newblock Number 2010,06 in Network architectures and services. Network
  Architectures and Services, Techn. Univ. M{\"u}nchen, M{\"u}nchen, 2010.
\newblock OCLC: 845870015.

\bibitem{shrivastava_application-aware_2011} Vivek Shrivastava, Petros Zerfos, Kang-Won Lee, Hani Jamjoom, Yew-Huey Liu, and
  Suman Banerjee.
\newblock Application-aware virtual machine migration in data centers.
\newblock In {\em {INFOCOM}, 2011 {Proceedings} {IEEE}}, pages 66--70. IEEE,
  2011.

\bibitem{georgopoulos_cache_2014} Panagiotis Georgopoulos, Matthew Broadbent, Bernhard Plattner, and Nicholas
  Race.
\newblock Cache as a service: {Leveraging} sdn to efficiently and transparently
  support video-on-demand on the last mile.
\newblock In {\em Computer {Communication} and {Networks} ({ICCCN}), 2014 23rd
  {International} {Conference} on}, pages 1--9. IEEE, 2014.

\bibitem{maddah-ali_fundamental_2014} Mohammad~Ali Maddah-Ali and Urs Niesen.
\newblock Fundamental limits of caching.
\newblock {\em IEEE Transactions on Information Theory}, 60(5):2856--2867,
  2014.

\bibitem{greenberg_cost_2008} Albert Greenberg, James Hamilton, David~A. Maltz, and Parveen Patel.
\newblock The cost of a cloud: research problems in data center networks.
\newblock {\em ACM SIGCOMM computer communication review}, 39(1):68--73, 2008.

\bibitem{xu_multi-objective_2010} Jing Xu and Jose A.~B. Fortes.
\newblock Multi-{Objective} {Virtual} {Machine} {Placement} in {Virtualized}
  {Data} {Center} {Environments}.
\newblock pages 179--188. IEEE, December 2010.

\bibitem{radhakrishnan_netshare_2012} Sivasankar Radhakrishnan, Rong Pan, Amin Vahdat, and George Varghese.
\newblock Netshare and stochastic netshare: predictable bandwidth allocation
  for data centers.
\newblock {\em ACM SIGCOMM Computer Communication Review}, 42(3):5--11, 2012.

\bibitem{benson_network_2010} Theophilus Benson, Aditya Akella, and David~A. Maltz.
\newblock Network traffic characteristics of data centers in the wild.
\newblock In {\em Proceedings of the 10th {ACM} {SIGCOMM} conference on
  {Internet} measurement}, pages 267--280. ACM, 2010.

\bibitem{krishnamurthy_passive_2010} Arvind Krishnamurthy and B.~Plattner, editors.
\newblock {\em Passive and active measurement: 11th international conference,
  {PAM} 2010, {Zurich}, {Switzerland}, {April} 7-9, 2010: proceedings}.
\newblock Number 6032 in Lecture notes in computer science. Springer, Berlin,
  2010.

\bibitem{stefanovici_software-defined_2015} Ioan Stefanovici, Eno Thereska, Greg O'Shea, Bianca Schroeder, Hitesh Ballani,
  Thomas Karagiannis, Antony Rowstron, and Tom Talpey.
\newblock Software-defined caching: managing caches in multi-tenant data
  centers.
\newblock pages 174--181. ACM Press, 2015.

\bibitem{singh_server-storage_2008} Aameek Singh, Madhukar Korupolu, and Dushmanta Mohapatra.
\newblock Server-storage virtualization: integration and load balancing in data
  centers.
\newblock In {\em Proceedings of the 2008 {ACM}/{IEEE} conference on
  {Supercomputing}}, page~53. IEEE Press, 2008.

\bibitem{lall_data_2006} Ashwin Lall, Vyas Sekar, Mitsunori Ogihara, Jun Xu, and Hui Zhang.
\newblock Data streaming algorithms for estimating entropy of network traffic.
\newblock In {\em {ACM} {SIGMETRICS} {Performance} {Evaluation} {Review}},
  volume~34, pages 145--156. ACM, 2006.

\bibitem{meng_improving_2010} Xiaoqiao Meng, Vasileios Pappas, and Li~Zhang.
\newblock Improving the scalability of data center networks with traffic-aware
  virtual machine placement.
\newblock In {\em {INFOCOM}, 2010 {Proceedings} {IEEE}}, pages 1--9. IEEE,
  2010.

\bibitem{jun_ddos_2014} Jae-Hyun Jun, Cheol-Woong Ahn, and Sung-Ho Kim.
\newblock {DDoS} attack detection by using packet sampling and flow features.
\newblock pages 711--712. ACM Press, 2014.

\bibitem{yu_flowsense:_2013} Curtis Yu, Cristian Lumezanu, Yueping Zhang, Vishal Singh, Guofei Jiang, and
  Harsha~V. Madhyastha.
\newblock Flowsense: {Monitoring} network utilization with zero measurement
  cost.
\newblock In {\em International {Conference} on {Passive} and {Active}
  {Network} {Measurement}}, pages 31--41. Springer, 2013.

\bibitem{al-fares_hedera:_2010} Mohammad Al-Fares, Sivasankar Radhakrishnan, Barath Raghavan, Nelson Huang, and
  Amin Vahdat.
\newblock Hedera: {Dynamic} flow scheduling for data center networks.
\newblock In {\em Nsdi}, volume~10, pages 19--19, 2010.

\bibitem{mori_identifying_2004} Tatsuya Mori, Masato Uchida, Ryoichi Kawahara, Jianping Pan, and Shigeki Goto.
\newblock Identifying elephant flows through periodically sampled packets.
\newblock In {\em Proceedings of the 4th {ACM} {SIGCOMM} conference on
  {Internet} measurement}, pages 115--120. ACM, 2004.

\bibitem{ros-giralt_mathematical_2017} Jordi Ros-Giralt, Alan Commike, Sourav Maji, and Malathi Veeraraghavan.
\newblock A {Mathematical} {Framework} for the {Detection} of {Elephant}
  {Flows}.
\newblock {\em arXiv preprint arXiv:1701.01683}, 2017.

\bibitem{lakhina_characterization_2004} Anukool Lakhina, Mark Crovella, and Christiphe Diot.
\newblock Characterization of network-wide anomalies in traffic flows.
\newblock In {\em Proceedings of the 4th {ACM} {SIGCOMM} conference on
  {Internet} measurement}, pages 201--206. ACM, 2004.

\bibitem{lorenz_optimal_2003} Dean~H. Lorenz, Ariel Orda, and Danny Raz.
\newblock Optimal partition of {QoS} requirements for many-to-many connections.
\newblock In {\em {INFOCOM} 2003. {Twenty}-{Second} {Annual} {Joint}
  {Conference} of the {IEEE} {Computer} and {Communications}. {IEEE}
  {Societies}}, volume~3, pages 1670--1679. IEEE, 2003.

\bibitem{noauthor_mice_2013} networkheresy ~.
\newblock Of {Mice} and {Elephants}, November 2013.

\bibitem{pettit_open_2014} Justin Pettit.
\newblock Open {vSwitch} and the {Intelligent} {Edge}, 2014.

\bibitem{zhu_intelligent_2015} Huikang Zhu, Hongbo Fan, Xuan Luo, and Yaohui Jin.
\newblock Intelligent timeout master: {Dynamic} timeout for {SDN}-based data
  centers.
\newblock In {\em Integrated {Network} {Management} ({IM}), 2015 {IFIP}/{IEEE}
  {International} {Symposium} on}, pages 734--737. IEEE, 2015.

\bibitem{wang_expeditus:_2017} Peng Wang, Hong Xu, Zhixiong Niu, Dongsu Han, and Yongqiang Xiong.
\newblock Expeditus: {Congestion}-{Aware} {Load} {Balancing} in {Clos} {Data}
  {Center} {Networks}.
\newblock {\em IEEE/ACM Transactions on Networking}, 25(5):3175--3188, October
  2017.

\bibitem{wilson_better_2011} Christo Wilson, Hitesh Ballani, Thomas Karagiannis, and Ant Rowtron.
\newblock Better never than late: {Meeting} deadlines in datacenter networks.
\newblock {\em ACM SIGCOMM Computer Communication Review}, 41(4):50--61, 2011.

\bibitem{mittal_timely:_2015} Radhika Mittal, David Zats, Vinh~The Lam, Nandita Dukkipati, Emily Blem, Hassan
  Wassel, Monia Ghobadi, Amin Vahdat, Yaogong Wang, and David Wetherall.
\newblock {TIMELY}: {RTT}-based {Congestion} {Control} for the {Datacenter}.
\newblock pages 537--550. ACM Press, 2015.

\bibitem{lorenz_optimal_2002} Dean~H. Lorenz and Ariel Orda.
\newblock Optimal partition of {QoS} requirements on unicast paths and
  multicast trees.
\newblock {\em ieee/acm Transactions on Networking}, 10(1):102--114, 2002.

\bibitem{bari_data_2013} Md~Faizul Bari, Raouf Boutaba, Rafael Esteves, Lisandro~Zambenedetti Granville,
  Maxim Podlesny, Md~Golam Rabbani, Qi~Zhang, and Mohamed~Faten Zhani.
\newblock Data center network virtualization: {A} survey.
\newblock {\em IEEE Communications Surveys \& Tutorials}, 15(2):909--928, 2013.

\bibitem{roy_inside_2015} Arjun Roy, Hongyi Zeng, Jasmeet Bagga, George Porter, and Alex~C. Snoeren.
\newblock Inside the {Social} {Network}'s ({Datacenter}) {Network}.
\newblock pages 123--137. ACM Press, 2015.

\bibitem{benson_understanding_2009} Theophilus Benson, Ashok Anand, Aditya Akella, and Ming Zhang.
\newblock Understanding data center traffic characteristics.
\newblock page~65. ACM Press, 2009.

\bibitem{ahmed_novel_2008} Ejaz Ahmed, Andrew Clark, and George Mohay.
\newblock A {Novel} {Sliding} {Window} {Based} {Change} {Detection} {Algorithm}
  for {Asymmetric} {Traffic}.
\newblock pages 168--175. IEEE, October 2008.

\bibitem{box_time_2016} George E.~P. Box, Gwilym~M. Jenkins, Gregory~C. Reinsel, and Greta~M. Ljung.
\newblock {\em Time series analysis: forecasting and control}.
\newblock Wiley series in probability and statistics. John Wiley \& Sons, Inc,
  Hoboken, New Jersey, fifth edition edition, 2016.

\bibitem{kalekar_time_2004} Prajakta~S. Kalekar.
\newblock Time series forecasting using holt-winters exponential smoothing.
\newblock {\em Kanwal Rekhi School of Information Technology}, 4329008:1--13,
  2004.

\bibitem{beloglazov_optimal_2012} Anton Beloglazov and Rajkumar Buyya.
\newblock Optimal online deterministic algorithms and adaptive heuristics for
  energy and performance efficient dynamic consolidation of virtual machines in
  {Cloud} data centers: {ENERGY} {AND} {PERFORMANCE} {EFFICIENT} {DYNAMIC}
  {CONSOLIDATION} {OF} {VIRTUAL} {MACHINES}.
\newblock {\em Concurrency and Computation: Practice and Experience},
  24(13):1397--1420, September 2012.

\bibitem{schulz-zander_opensdwn:_2015} Julius Schulz-Zander, Carlos Mayer, Bogdan Ciobotaru, Stefan Schmid, and Anja
  Feldmann.
\newblock {OpenSDWN}: {Programmatic} {Control} over {Home} and {Enterprise}
  {WiFi}.
\newblock In {\em Proceedings of the 1st {ACM} {SIGCOMM} {Symposium} on
  {Software} {Defined} {Networking} {Research}}, {SOSR} '15, pages 16:1--16:12,
  New York, NY, USA, 2015. ACM.

\bibitem{clemm_data_2017} Alexander Clemm, Jan Medved, Robert Varga, Nitin Bahadur, Hariharan
  Ananthakrishnan, and Xufeng Liu.
\newblock A {Data} {Model} for {Network} {Topologies}.
\newblock Internet-{Draft} draft-ietf-i2rs-yang-network-topo-20, Internet
  Engineering Task Force, December 2017.

\bibitem{jurgen_schonwalder_network_2012} {J{\"u}rgen Sch{\"o}nw{\"a}lder}.
\newblock Network {Configuration} {Management} with {NETCONF} and {YANG}, July
  2012.

\bibitem{bjorklund_yang_2010} Martin Bjorklund.
\newblock {\em {YANG} - {A} {Data} {Modeling} {Language} for the {Network}
  {Configuration} {Protocol} ({NETCONF})}.
\newblock Number 6020 in Request for {Comments}. RFC Editor, October 2010.
\newblock Published: RFC 6020.

\bibitem{enns_network_2011} Rob Enns, Martin Bjorklund, Andy Bierman, and J{\"u}rgen Sch{\"o}nw{\"a}lder.
\newblock {\em Network {Configuration} {Protocol} ({NETCONF})}.
\newblock Number 6241 in Request for {Comments}. RFC Editor, June 2011.
\newblock Published: RFC 6241.

\bibitem{maxim_novak_serialization_2014} {Maxim Novak}.
\newblock Serialization {Performance} comparison ({C}\#/.{NET}) {\textendash}
  {Formats} \& {Frameworks} ({XML}{\textendash}{DataContractSerializer} \&
  {XmlSerializer}, {BinaryFormatter}, {JSON}{\textendash} {Newtonsoft} \&
  {ServiceStack}.{Text}, {Protobuf}, {MsgPack}), March 2014.

\bibitem{bruno_krebs_beating_nodate} {Bruno Krebs}.
\newblock Beating {JSON} performance with {Protobuf}.

\bibitem{ahmad_arima_2013} Wan Kamarul Ariffin~Wan Ahmad and Sabri Ahmad.
\newblock Arima model and exponential smoothing method: {A} comparison.
\newblock {\em AIP Conference Proceedings}, 1522(1):1312--1321, 2013.

\bibitem{hyndman_another_2006} Rob~J. Hyndman and Anne~B. Koehler.
\newblock Another look at measures of forecast accuracy.
\newblock {\em International Journal of Forecasting}, 22(4):679 -- 688, 2006.

\bibitem{choudhary_runtime-efficacy_2017} Dhruv Choudhary, Arun Kejariwal, and Francois Orsini.
\newblock On the {Runtime}-{Efficacy} {Trade}-off of {Anomaly} {Detection}
  {Techniques} for {Real}-{Time} {Streaming} {Data}.
\newblock {\em arXiv preprint arXiv:1710.04735}, 2017.


\end{thebibliography}

%%%%% CLEAR DOUBLE PAGE!
\newpage{\pagestyle{empty}\cleardoublepage}